### 2019-09-30 conflog.tex
updates from Katy

We propose the conference be held on the following dates: 
\begin{enumerate}
	\item Thursday, April 8$^{th}$ - Sunday, April 11$^{th}$ 
	\item Thursday, April 15$^{th}$ - Sunday, April 18$^{th}$
\end{enumerate}
We believe either of these dates would serve as an appropriate first choice because they avoid major conflict dates like finals and spring break for most schools. Additionally, mid-April offers pleasant, mild, weather in Champaign. The reason for proposing two weekends to host the conference is due to the UIUC tradition of hosting Mom's Weekend on or near the first weekend in April. The Illinois Mom's Association has not yet announced their 2021 dates but, to avoid potential conflict, we suggest two dates. In the event that both of these dates are unavailable our backup date is 
\begin{itemize}
	\item Thursday, April 1$^{st}$ - Sunday, April 4$^{th}$.  
\end{itemize}
This is a backup date because Easter falls on that Sunday. In general, this should be avoided. In this case we found that holding the conference at the end of April would conflict with finals for students and holding it earlier in March would conflict with several spring breaks as well as having potentially poorer weather. A detailed conflict schedule is listed in Appendix A.

@@

\subsection{Banquet Space}
\subsubsection{Garden Hotel in Urbana}
The opening ceremony dinner on Thursday night will be hosted at the Garden Hotel in Urbana. They have a capacity of 600 people in rounds and offer in house catering as well as AV capabilities. This location was chosen for its convenience, as it would be the primary hotel for the conference.

@@

\subsubsection{IHotel}
Dinner on Friday night will be hosted at the IHotel. The IHotel is undergoing an expansion that will increase the capacity of their banquet space to 690 people in rounds. This expansion is set to be completed by Fall 2020. We will be hosting a social at the 77 Club in Memorial Stadium, just up the street. Information about the IHotel expansion is included in Appendix D.

@@

\subsubsection{Illini Union}
After the career fair is taken down on Saturday the final dinner will be set up in the combined Illini Rooms, which has a seating capacity of 496 people in rounds. Catering will be provided by Universiy Catering which allows us to avoid the 20\% gratuity for services.\\

@@

\subsection{Conference Contingency Plan}
In the event that the Union has reduced availability during the conference we have the ability to host technical sessions and workshops at a combination of buildings: The National Center for Supercomputing Applications (NCSA) and Beckman Institute. These two buildings have large capacity rooms and small capacity rooms. As these buildings are UIUC property, the cost of renting them are significantly reduced compared to a private facility. Additionally, these two buildings are adjacent to one another and are at most a 10 minute walk from the Union. We could also host all technical sessions at the IHotel. Hosting at the IHotel is more expensive than hosting in University buildings and would also require additional transportation options. We would need to reevaluate some parts of our budget in order to host the technical program at this venue. See Appendix E for a map marking the locations of the proposed conference facilities.\\

@@

\textbf{Beckman Institute}
The Beckman Institute for Advanced Science and Technology at the University of Illinois is an interdisciplinary research institute devoted to leading-edge research in the physical sciences, computation, engineering, biology, behavior, cognition, and neuroscience.\\

@@

{\centering
\begin{tabular}{lccccc}
\hline\hline
\textbf{Hotel} & \textbf{Distance from the Union (mi)} & \textbf{Dates} & \textbf{Number of Rooms} & \textbf{Rates*} & \textbf{Per Person**}\\
\hline\hline
Garden Urbana & 2.2  & 4/8-4/11 & 198 & 119 & $\$$29.75\\
Illini Union & 0.0 & 4/8-4/11 & 35 & 134 & $\$$33.5\\
Marriott TowneSuites &0.25 & 4/8-4/11 & 95 & 189 & \$47.50\\ 
\end{tabular}}
\textbf{*}\textit{Price for a queen double}
\textbf{**}\textit{Assumes 4 people per room}

@@

\subsubsection{Getting to Champaign}
The University of Illinois is a 2.5 hour drive from one of the largest airports in the world, O'Hare International Airport. There is also a small airport located just 20 minutes outside of campus. Additionally, there is a reliable bus service, Peoria Charter, that runs between O'Hare and the UIUC campus several times per day. Below are the round-trip, non-stop, airfare costs for the first weekend of April. Peoria Charter fare from O'Hare to UIUC is currently $\$61$ round-trip.

\begin{center}
   \begin{tabular}{lccc}
   	\hline\hline
    \textbf{School} & \textbf{Departure City} & \textbf{O'Hare (ORD)*} & \textbf{Willard (CMI)} \\
    \hline\hline
    University of California - Berkeley & San Francisco (SFO) & $\$$338 & $\$$436 \\
    University of California - Irvine&Orange County (SNA)&$\$$394&$\$$436\\
    Colorado School of Mines & Denver (DEN) & $\$$222 & $\$$328 \\
    Three Rivers Community College & Hartford (BDL) & $\$$468 & $\$$327 \\ 
    University of Florida & Gainesville (GNV)& $\$$377 & $\$$416 \\
    Georgia Institute of Technology & Atlanta (ATL)& $\$$199 & $\$$291 \\
    Southern Polytechnic State University & Atlanta (ATL) & $\$$199 & $\$$291 \\
    Idaho State University & Idaho Falls (IDA) & $\$$501 & NA \\
    Kansas State University & Manhattan (MHK) & $\$$336 & $\$$406 \\ 
    Louisiana State University & Baton Roughe (BTR) & $\$$380 & $\$$329 \\
    United States Naval Academy & Hanover (BWI) & $\$$210 & $\$$321 \\  
    University of Maryland & Hanover (BWI)&$\$$210 &$\$$321 \\ 
    Massachusetts Institute of Technology & Boston (BOS)&$\$$191 &$\$$325 \\ 
    University of Massachusetts - Lowell &Boston (BOS) &$\$$191 &$\$$325 \\
    University of Nevada - Las Vegas & Las Vegas (LAS)& $\$$262 &$\$$358 \\ 
    University of New Mexico &Albuquerque (ABQ) &$\$$439 &$\$$358 \\ 
    City College of New York &$\$$New York (JFK) &$\$$245 &$\$$325 \\
    Excelsior College & Albany (ALB) &$\$$444 &$\$$327 \\ 
    Rensselaer Polytechnic Institute & Albany (ALB)&$\$$444 &$\$$327 \\ 
    United States Military Academy at West Point&New Windsor (SWF)&$\$$273 &$\$$357 \\ 
    North Carolina State University &Morrisville (RDU) &$\$$180 &$\$$321 \\
    Oregon State University &Portland (PDX) &$\$$314 &$\$$436 \\ 
    Pennsylvania State University & Harrisburg (MDT)&$\$$397 & $\$$323 \\
    University of Pittsburgh &Pittsburgh (PIT) &$\$$282 &$\$$293 \\ 
    Clemson University&Greenville (GSP)&$\$$356&$\$$287\\
    South Carolina State University&Columbia (CAE)&$\$$407 &$\$$564 \\ 
    University of South Carolina&Columbia (CAE)&$\$$407&$\$$564\\
    Chattanooga State Comunity College&Chattanooga (CHA)&$\$$334&$\$$316\\
    University of Tennessee&Knoxville (TYS)&$\$$340&$\$$291\\
    Texas A\&M University&College Station (CLL)&$\$$367&$\$$243\\
    University of Texas - Arlington&Dallas (DFW)&$\$$197&$\$$303\\
    University of Texas - Austin&Austin (AUS)&$\$$298&$\$$358\\
    University of Texas - Permian Basin&Midland (MAF)&$\$$434&$\$$333\\
    Utah State University&Salt Lake City (SLC)&$\$$298&$\$$358\\
    University of Utah&Salt Lake City (SLC)&$\$$298&$\$$358\\
    Virginia Commonwealth University&Richmond (RIC)&$\$$279&$\$$321\\
    University of Washington&Seattle (SEA)&$\$$253&$\$$436\\
    \hline
    Average Lowest Cost for Air Travel**&$\$$293&&
    \end{tabular} 
\end{center}
\textbf{*}\textit{A \$61 round-trip bus ticket through Peoria Charter was added to the cost.}\\
\textbf{**}\textit{The average of the lowest price between O'Hare and Willard.}\\

Due to the central location of UIUC, driving might be a good option for some schools and individuals. Below are the approximate driving times from several universities.

\begin{center}
   \begin{tabular}{lcccc}
   \hline\hline
   \textbf{School}&\textbf{Estimated Mileage (mi)}&\textbf{Driving Time (hrs)}&\textbf{Fuel Cost*}&\textbf{Per Person**}\\
   \hline\hline
    Purdue University&90&1h 40m&\$21.86&\$5.47\\
    University of Cincinnati&233& 3h 40m&\$56.60&\$14.15\\
    Air Force Tech &250&3h 58m&\$60.73&\$15.18\\
    University of Wisconsin&253&4h&\$61.46&\$15.36\\
    Missouri University S \& T &279&4h 21m&\$67.77&\$16.94\\
    U. Missouri - Columbia&291&4h 28m&\$70.69&\$17.67\\
    Ohio State University&302&4h 47m&\$73.36&\$18.34\\
    University of Michigan&345&5h 17m&\$83.81&\$20.95\\
    Vanderbilt University&373&5h 33m&\$90.61&\$22.65\\
    Iowa State University&378&5h 44m&\$91.82&\$22.96\\
    \hline
    Average&279&4h 22m&\$67.87&\$16.97

    \end{tabular} 
\end{center}
\textbf{*}\textit{Estimated assuming an average 23 MPG}\\
\textbf{**}\textit{Assumes four people in a car}

@@

>>>>

We propose the conference be held on either of the following dates: 
\begin{enumerate}
	\item Thursday, April 8$^{th}$ - Sunday, April 11$^{th}$ 
	\item Thursday, April 15$^{th}$ - Sunday, April 18$^{th}$
\end{enumerate}
We believe either of these dates would serve as an appropriate first choice because they avoid major conflict dates like finals and spring break for most schools. Additionally, mid-April offers pleasant, mild, weather in Champaign. The reason for proposing two weekends to host the conference is due to the UIUC tradition of hosting Mom's Weekend on or near the first weekend in April. The Illinois Mom's Association has not yet announced their 2021 dates but, to avoid potential conflict, we suggest two dates. In the event that both of these dates are unavailable our backup date is 
\begin{itemize}
	\item Thursday, April 1$^{st}$ - Sunday, April 4$^{th}$.  
\end{itemize}
This is a backup date because Easter falls on that Sunday. In general, this should be avoided. In this case we found that holding the conference at the end of April would conflict with finals for students and holding it earlier in March would conflict with several spring breaks as well as having potentially poorer weather. A detailed conflict schedule is listed in Appendix A.

@@

\subsection{Banquet Space}
\subsubsection{Garden Hotel in Urbana}
The opening ceremony dinner on Thursday night will be hosted at the Garden Hotel in Urbana. It has a seating capacity of 600 people in rounds and offer in house catering as well as AV capabilities. This location was chosen for its convenience, as it would be the primary hotel for the conference.

@@

\subsubsection{I Hotel}
Dinner on Friday night will be hosted at the I Hotel. The I Hotel is undergoing an expansion that will increase the capacity of their banquet space to 690 people in rounds. Catering is provided by University Catering which avoids a 20\% gratuity charge because of its association with the University of Illinois. This expansion is set to be completed by Fall 2020. We will be hosting a social at the 77 Club in Memorial Stadium, just up the street. Information about the I Hotel expansion is included in Appendix D.

@@

\subsubsection{Illini Union}
After the career fair is taken down on Saturday the final dinner will be set up in the combined Illini Rooms, which has a seating capacity of 496 people in rounds. Catering will be provided by Universiy Catering which allows us to avoid the 20\% gratuity for services. A floorplan for the Illini Rooms in rounds is available in Appendix D.\\

@@

\subsection{Conference Contingency Plan}
In the event that the Union has reduced availability during the conference we have the ability to host technical sessions and workshops at a combination of buildings: The National Center for Supercomputing Applications (NCSA) and Beckman Institute. Rooms in Beckman Institute range from 20 - 60 classroom capacity. Most rooms have A/V capabilities. NCSA has rooms that can hold 13 - 50 people in lecture style. As these buildings are UIUC property, the cost of renting them are significantly reduced compared to a private facility. Additionally, these two buildings are adjacent to one another and are at most a 10 minute walk from the Union. We could also host all technical sessions at the I Hotel. Hosting at the I Hotel is more expensive than hosting in University buildings and would also require additional transportation options. We would need to reevaluate some parts of our budget in order to host the technical program at this venue. See Appendix E for a map marking the locations of the proposed conference facilities.\\

@@

\textbf{Beckman Institute}\\
The Beckman Institute for Advanced Science and Technology at the University of Illinois is an interdisciplinary research institute devoted to leading-edge research in the physical sciences, computation, engineering, biology, behavior, cognition, and neuroscience.\\

@@

{\centering
\begin{tabular}{lccccc}
\hline\hline
\textbf{Hotel} & \textbf{Distance from the Union (mi)} & \textbf{Dates} & \textbf{Number of Rooms} & \textbf{Rates*} & \textbf{Per Person**}\\
\hline\hline
Garden Urbana & 2.2  & 4/8-4/11 & 198 & 119 & $\$$29.75\\
Illini Union & 0.0 & 4/8-4/11 & 35 & 134 & $\$$33.5\\
Marriott TowneSuites &0.25 & 4/8-4/11 & 95 & 189 & \$47.50\\ 
\hline
\end{tabular}}
\textbf{*}\textit{Price for a queen double}
\textbf{**}\textit{Assumes 4 people per room}

@@

\subsubsection{Getting to Champaign}
The University of Illinois is a 2.5 hour drive from one of the largest airports in the world, O'Hare International Airport. There is also a small airport located just 20 minutes outside of campus. Additionally, there is a reliable bus service, Peoria Charter, that runs between O'Hare and the UIUC campus several times per day. Table \ref{table:airfare} shows the round-trip, non-stop, airfare costs for the first weekend of April. Peoria Charter fare from O'Hare to UIUC is currently $\$61$ round-trip. Due to the central location of UIUC, driving might be a good option for some schools and individuals. Table \ref{table:ground} shows the approximate driving times and costs from several universities.

\begin{table}[H]
\caption{Estimated Costs of Ground Travel}
\label{table:ground}
   \begin{tabular}{lcccc}
   \hline\hline
   \textbf{School}&\textbf{Estimated Mileage (mi)}&\textbf{Driving Time (hrs)}&\textbf{Fuel Cost*}&\textbf{Per Person**}\\
   \hline\hline
    Purdue University&90&1h 40m&\$21.86&\$5.47\\
    University of Cincinnati&233& 3h 40m&\$56.60&\$14.15\\
    Air Force Tech &250&3h 58m&\$60.73&\$15.18\\
    University of Wisconsin&253&4h&\$61.46&\$15.36\\
    Missouri University S \& T &279&4h 21m&\$67.77&\$16.94\\
    U. Missouri - Columbia&291&4h 28m&\$70.69&\$17.67\\
    Ohio State University&302&4h 47m&\$73.36&\$18.34\\
    University of Michigan&345&5h 17m&\$83.81&\$20.95\\
    Vanderbilt University&373&5h 33m&\$90.61&\$22.65\\
    Iowa State University&378&5h 44m&\$91.82&\$22.96\\
    \hline
    Average&279&4h 22m&\$67.87&\$16.97

    \end{tabular} 
\end{table}
\noindent\textbf{*}\textit{Estimated assuming an average 23 MPG}\\
\textbf{**}\textit{Assumes four people in a car}

@@

\begin{table}[H]
\caption{Airfare to Chicago/Champaign}
\label{table:airfare}
   \begin{tabular}{lccc}
   	\hline\hline
    \textbf{School} & \textbf{Departure City} & \textbf{O'Hare (ORD)*} & \textbf{Willard (CMI)} \\
    \hline\hline
    University of California - Berkeley & San Francisco (SFO) & $\$$338 & $\$$436 \\
    University of California - Irvine&Orange County (SNA)&$\$$394&$\$$436\\
    Colorado School of Mines & Denver (DEN) & $\$$222 & $\$$328 \\
    Three Rivers Community College & Hartford (BDL) & $\$$468 & $\$$327 \\ 
    University of Florida & Gainesville (GNV)& $\$$377 & $\$$416 \\
    Georgia Institute of Technology & Atlanta (ATL)& $\$$199 & $\$$291 \\
    Southern Polytechnic State University & Atlanta (ATL) & $\$$199 & $\$$291 \\
    Idaho State University & Idaho Falls (IDA) & $\$$501 & NA \\
    Kansas State University & Manhattan (MHK) & $\$$336 & $\$$406 \\ 
    Louisiana State University & Baton Roughe (BTR) & $\$$380 & $\$$329 \\
    United States Naval Academy & Hanover (BWI) & $\$$210 & $\$$321 \\  
    University of Maryland & Hanover (BWI)&$\$$210 &$\$$321 \\ 
    Massachusetts Institute of Technology & Boston (BOS)&$\$$191 &$\$$325 \\ 
    University of Massachusetts - Lowell &Boston (BOS) &$\$$191 &$\$$325 \\
    University of Nevada - Las Vegas & Las Vegas (LAS)& $\$$262 &$\$$358 \\ 
    University of New Mexico &Albuquerque (ABQ) &$\$$439 &$\$$358 \\ 
    City College of New York &$\$$New York (JFK) &$\$$245 &$\$$325 \\
    Excelsior College & Albany (ALB) &$\$$444 &$\$$327 \\ 
    Rensselaer Polytechnic Institute & Albany (ALB)&$\$$444 &$\$$327 \\ 
    United States Military Academy at West Point&New Windsor (SWF)&$\$$273 &$\$$357 \\ 
    North Carolina State University &Morrisville (RDU) &$\$$180 &$\$$321 \\
    Oregon State University &Portland (PDX) &$\$$314 &$\$$436 \\ 
    Pennsylvania State University & Harrisburg (MDT)&$\$$397 & $\$$323 \\
    University of Pittsburgh &Pittsburgh (PIT) &$\$$282 &$\$$293 \\ 
    Clemson University&Greenville (GSP)&$\$$356&$\$$287\\
    South Carolina State University&Columbia (CAE)&$\$$407 &$\$$564 \\ 
    University of South Carolina&Columbia (CAE)&$\$$407&$\$$564\\
    Chattanooga State Comunity College&Chattanooga (CHA)&$\$$334&$\$$316\\
    University of Tennessee&Knoxville (TYS)&$\$$340&$\$$291\\
    Texas A\&M University&College Station (CLL)&$\$$367&$\$$243\\
    University of Texas - Arlington&Dallas (DFW)&$\$$197&$\$$303\\
    University of Texas - Austin&Austin (AUS)&$\$$298&$\$$358\\
    University of Texas - Permian Basin&Midland (MAF)&$\$$434&$\$$333\\
    Utah State University&Salt Lake City (SLC)&$\$$298&$\$$358\\
    University of Utah&Salt Lake City (SLC)&$\$$298&$\$$358\\
    Virginia Commonwealth University&Richmond (RIC)&$\$$279&$\$$321\\
    University of Washington&Seattle (SEA)&$\$$253&$\$$436\\
    \hline
    Average Lowest Cost for Air Travel**&$\$$293&&
    \end{tabular} 
\end{table}

\noindent\textbf{*}\textit{A \$61 round-trip bus ticket through Peoria Charter was added to the cost.}\\
\textbf{**}\textit{The average of the lowest price between O'Hare and Willard.}\\

### 2019-09-30 theme.tex
updates from Katy

\section{Saving the World One Atom at a Time}
The future is nuclear.\\
There are many challenges facing the world today and some have been designated existential threats to humanity. Young people today will witness the growing toll of anthropogenic climate change. As students, obstacles at the scale of the world climate crisis appear daunting and overwhelming. We believe that many solutions will come from the nuclear sciences. The ANS Student Conference is an opportunity for students and professionals to come together and share advances in critical technology and research, dedicated to solving these problems. Nuclear, plasma, and radiological engineering will be central to many endeavors. Whether the goal is solving the world’s energy needs, developing technology that will take us to the stars, or curing cancer. By hosting this conference, we hope to inspire and motivate students in nuclear, plasma, and radiological engineering fields to tackle big problems. Saving the World One Atom at a Time reflects the fact that nuclear science is a powerful force in dealing with grand challenge problems. This theme also honors the individual, atomic, contributions from students, researchers, and professionals that are essential to progress. This conference is about science and it is about the people that make science possible. Students will hear from visionary speakers and leaders of the nuclear science community and come away with optimism for the future; knowing that they are saving the world one atom at a time.\\
There are three main goals of our theme and each of these goals will be the focus of a different day of the student conference.
\begin{enumerate}
	\item Celebrate the people behind the science\\
	Everyone that does science has a unique background, skillset, and experiences. People are what make science possible. Encouraging diversity and inclusivity in these areas, and others, improve creativity, productivity, and insights. We showcase this aspect of the conference with panels like \textit{Science is People: How to Conduct Inclusive Research} and \textit{Scientific Storytelling}.
	\item Help students and professionals develop a strong network of like-minded people.\\
	This is the networking and professional-development-focused section of the conference. Beyond the mere job-seeking aspect, these networks enable the spread of ideas. Additionally, this night builds on top of the previous night as we remember that our networks also consist of people. Better networks are more diverse. This aspect of the conference is captured by workshops like \textit{Developing Your Network}. 
	\item Inspire young students to take on grand challenge problems\\
	The final day is the culmination of the conference and the single unifying ideal. For many students, this conference might be the first time they are presenting research to their peers, mentors, and future employers. Everything about this conference should encourage students to take on challenges that seem bigger than they are in order to better the world around them. 
\end{enumerate}
These goals and our theme motivated every decision in our conference proposal. The University of Illinois at Urbana-Champaign chapter of ANS would be honored to host the 2021 student conference. We hope to create an atmosphere that will galvanize students and professionals for the exciting future of nuclear engineering.\\

>>>>

\section{Saving the World One Atom at a Time}
The future is nuclear. There are many grand challenges facing the world today and some have been designated existential threats to humanity. Young people today will witness the growing toll of anthropogenic climate change. As students, obstacles at the scale of the world climate crisis appear daunting and overwhelming. We believe that many solutions will come from the nuclear sciences. The ANS Student Conference is an opportunity for students and professionals to come together and share advances in critical technology and research dedicated to solving these problems. Nuclear, plasma, and radiological engineering will be central to many endeavors, whether the goal is solving the world’s energy needs, developing technology that will take us to the stars, or curing cancer. By hosting this conference, we hope to inspire and motivate students in nuclear, plasma, and radiological engineering to tackle big problems. Saving the World One Atom at a Time reflects the fact that nuclear science is a powerful force in dealing with grand challenge problems. This theme also honors the individual, atomic, contributions from students, researchers, and professionals that are essential to progress. This conference is about science and engineering and it is about the people that make science possible. Students will hear from visionary speakers and leaders of the nuclear science community and come away with optimism for the future; knowing that they are saving the world one atom at a time.\\
There are three main goals of our theme and each of these goals will be the focus of a different day of the student conference.
\begin{enumerate}
	\item Celebrate the people behind the science and engineering.\\
	Everyone that does science has a unique background, skillset, and experiences. People are what make science possible. Encouraging diversity and inclusivity in these areas, and others, improve creativity, productivity, and insights. We showcase this aspect of the conference with panels like \textit{Science is People: How to Conduct Inclusive Research} and \textit{Scientific Storytelling}.
	\item Help students and professionals develop a strong network of like-minded people.\\
	This is the networking and professional-development-focused section of the conference. Beyond the mere job-seeking aspect, these networks enable the spread of ideas. Additionally, this evening builds on top of the previous night as we remember that our networks also consist of people. More diverse networks are better networks. This aspect of the conference is captured by workshops like \textit{Developing Your Network}. 
	\item Inspire the next generation of nuclear engineers to take on grand challenge problems\\
	The final day is the culmination of the conference underpins the single unifying ideal. For many students, this conference might be the first time they are presenting research to their peers, mentors, and future employers. Everything about this conference should encourage students to take on challenges that seem bigger than they are in order to improve the world around them.  
\end{enumerate}
These goals and our theme motivated every decision in our conference proposal. The University of Illinois at Urbana-Champaign chapter of ANS would be honored to host the 2021 student conference. We hope to create an atmosphere that will galvanize students and professionals for the exciting future of nuclear engineering.\\
